---
title: "TDS Project"
author: "David, Ross, Malo, Ellie, James"
date: "18/03/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
```

# Malignant Melanoma Prediction on UK Biobank

## Introduction 
* Incidence of melanoma 
* Motivation: Poor outcomes if detected late: conversely, early detection offers reduction in morbidity, increased treatment options and lower cost of full treatment.   
* No national screening programme yet specific for melanoma, current methods of detection via self-reporting or skin visual inspection by GP  
* Various models for predicting melanoma but none in clinical application yet  

## Methods  

* UK Biobank data ~ 500,000 participants 
* Cases selected as melanomas present at enrolment and incident cases 
  - ~5,000 cases 
* Controls matched to cases at a 2:1 rate by age at recruitment and sex  
  - ~10,000 controls 
* Descriptive analytics looking into common demographic variables  
  - Using a priori knowledge we included other variables 
  - Sun exposure etc 
* Multiple univariate logistic regression was performed each of the “descriptive” features 
* Using ICD9/ICD10 biobank and HESIN data we one hot encoded sample for comorbidities 
  - We only considered diagnoses occuring before first recorded hospital episode with melanoma 
  - This was linked to the case/control matching 
  - 3 Different datasets of 1, 3 and 5 years prior to melanoma diagnosis were considered 

## Results

Table 1 

```{r table_1, echo = FALSE}
# very hacky table 1
tableone <- data.frame(matrix(ncol = 3, nrow=4))
colnames(tableone) <- c("Feature", "Cases", "Controls")
rownames(tableone) <-c("Age", "Sex","Mean Deprivation", "Skin Color")
kable(tableone)

```



## Discussion

## Conclusion

## References